Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
11.04

	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

>>>>

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
11.04

	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also assumed that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, the mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase behaviour accurately.

@@

	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}. This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.

@@

	As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases. The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$. As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore. The solute then diffuses through the film around the particle and reaches bulk concentration $c_f$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined if the relationship between the solute concentration in one phase and its equilibrium concentration is known.

		\begin{figure}[h!]
			\centering
			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=\columnwidth]{Figures/SFE_PFD.drawio.png}	
			\caption{The extraction mechanism}
			\label{fig: SFE_Mechanism}
		\end{figure}

@@

		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate is $r_e\left(c_s - c^*_p(c_f)\right)$ or more precisely

@@

		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up. The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.

@@

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content $c_{s0}$. As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable. Considering that it is assumed that the $c_{f0}=0$. Moreover, it is considered that the extractor is isothermal. %and described by ${\color{black}h_0}$. 
		Therefore, the initial and boundary conditions employed in the simulation are:

@@

		As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem. The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary. That quantity is conserved and neither produced nor consumed inside the control volume. For a derivative to be conservative, it must form a telescoping series. In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out. Discretization is applied to the conservative form of the process model to ensure mass conservation.

>>>>

	%The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. 
	This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also assumed that the thermodynamic pressure remains constant throughout the device. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.

@@

	%In this study, the kinetic term is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}. This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.

@@

	As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases. The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$. As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore. Then the solute diffuses through the film around the particle and reaches bulk concentration $c_f$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.

		\begin{figure}[h!]
			\centering
			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
			\caption{The mass transfer mechanism}
			\label{fig: SFE_Mechanism}
		\end{figure}

@@

		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}

@@

		The process yield is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up. The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.

@@

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content $c_{s0}$. As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable. Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal. %and described by ${\color{black}h_0}$. 
		Therefore, the initial and boundary conditions are define as follow:

@@

		%As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem. The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary. That quantity is conserved and neither produced nor consumed inside the control volume. 
		For a derivative to be conservative, it must form a telescoping series. In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out. The discretization is applied to the conservative form of the model to ensure mass conservation.

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
11.04

	\begin{figure*}[!h]
		\centering
		\begin{subfigure}{0.3\textwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.3\textwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.3\textwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma}
	\end{figure*}

@@

@@

@@

@@

>>>>

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
			\caption{The linear kinetic model \\ ~}
			\label{fig: Fit_1_linear}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
			\caption{The reduced linear kinetic model with axial diffusion}
			\label{fig: Fit_1_Di_Dx}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
			\caption{The modified model}
			\label{fig: Fit_1_Di_Gamma}
		\end{subfigure}
		\caption{Parameter space for experiment 1}
		%\label{fig: Fit_Di_Gamma}
	\end{figure}

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma_correlation}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma_correlation}
	\end{figure}

@@

	%The parameter estimation results are compared to the work of \citet{Povh2001}, who fitted the Sovova model to the same dataset. It should be noted that the \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments as explained above. Contrary to this work, \citet{Povh2001} has not used any numerical solver in his work but rather a combination of analytical methods and a trial and error procedure. \citet{Povh2001} stated that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters found in this work seem to have a physical interpretation, and their values are in the excerpted range.

	%\citet{Rahimi2011} fitted the same dataset to a model with desorption–dissolution–diffusion mechanism. To decrease the number of parameters to be found, \citet{Rahimi2011} applied a set of correlations. The remaining parameters were found using a genetic algorithm to solve the parameter estimation problem for each experiment separately. The results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model cannot reproduce the yield data. The desorption–dissolution–diffusion model and the model used in this work are structurally similar, with the main difference of $\gamma$ function. The $\gamma$ function increases the model's flexibility and allows it to obtain a better fit.

	%For every single experiment, \citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset. It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments. In contrast to this work, \citet{Povh2001} did not utilize numerical solvers but used a mix of analytical methodologies and trial-and-error procedures. \citet{Povh2001} remarked that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters identified in this study seem to have a physical interpretation and are within the expected range.

	\citet{Rahimi2011} analysed the same dataset using the desorption–dissolution–diffusion model. To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations. The remaining parameters were determined through the use of a genetic algorithm to solve the parameter estimation problem for each experiment individually. Results obtained by \citet{Rahimi2011} shows that the desorption–dissolution–diffusion model fails to reproduce the yield data. The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$ function. The $\gamma$ function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.

	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every single experiment. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
11.04

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the supercritical extraction process of essential oil from chamomile flowers.  Essential oils of chamomile are used extensively for medicinal purposes. Many different products of chamomile have been developed, the most popular of which is in the form of herbal tea. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data, with the assumption of normally distributed errors. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.

@@

\subsection{Governing equations} \label{CH:Governing_equations_chapter}
	The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}. Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section. This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor. According to this assumption, velocity and other flow properties change solely in the flow direction.

	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}. The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.

@@

Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed. The analysis follows the work of \citet{Schreier1982}.

@@

\begin{figure*}[!b]
	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
		\caption{Parameter space: the linear kinetic model}
		\label{fig: Fit_1_linear}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
		\caption{Parameter space: the reduced linear kinetic model with axial diffusion}
		\label{fig: Fit_1_Di_Dx}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
		\caption{Parameter space: the modified model}
		\label{fig: Fit_1_Di_Gamma}
	\end{subfigure}
	\caption{Parameter estimation results for experiment 1}
	%\label{fig: Fit_Di_Gamma}
\end{figure*}

@@

\begin{figure*}[!h]
	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
		\label{fig: Fit_1_4_Di_Gamma_correlation}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
		\label{fig: Fit_5_8_Di_Gamma_correlation}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
		\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
		\label{fig: Fit_9_12_Di_Gamma_correlation}
	\end{subfigure}
	\caption{Parameter estimation results}
	\label{fig: Fit_Di_Gamma_correlation}
\end{figure*}

@@

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
%\clearpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

@@

\subsection{Governing equations}
\subfile{Sections/Gouverning_equation_derivation}

@@

\subsection{Maximum likelihood} \label{CH: ML}
\subfile{Sections/Likelihood}

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the supercritical extraction process of essential oil from chamomile flowers.  Essential oils of chamomile are used extensively for medicinal purposes. Many different products of chamomile have been developed, the most popular of which is in the form of herbal tea. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated based on the Peng-Robinson equation of state. Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.

@@

\subsection{Governing equations} \label{CH:Governing_equations_chapter}
	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived. Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section. This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor. According to this assumption, velocity and other flow properties change solely in the flow direction.

	As discussed by \citet{Anderson2023}, all flows are compressible but some of them can be treated as incompressible when the Mach number is smaller than 0.3. This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The restraint allows for the removal of acoustic waves, and allows for large perturbations in density and/or temperature. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

	%The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.

	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}. %The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.

@@

\begin{comment}
Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed. The analysis follows the work of \citet{Schreier1982}.

@@

@@

@@

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
\clearpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

@@

%\subsection{Governing equations}
%\subfile{Sections/Gouverning_equation_derivation}

@@

%\subsection{Maximum likelihood} \label{CH: ML}
%\subfile{Sections/Likelihood}
